Weighted Model Counting with Conditional Weights

### 2020-08-17 paper/paper.tex
Fix a bug in parsing experimental data

\begin{table}
  \centering
  \caption{The numbers of instances (out of 1451) solved by ADDMC with each
    encoding (uniquely, faster than with others, and in total) under the
    described time and memory constraints}%
  \begin{tabular}{lrrr}
    \toprule
    Encoding & Unique & Fastest & Total \\
    \midrule
    \texttt{cd05} & 2 & 76 & 380 \\
    \texttt{cd06} & 0 & 214 & 363 \\
    \texttt{cw} & 234 & 633 & 965 \\
    \texttt{d02} & 40 & 58 & 782 \\
    \texttt{sbk05} & 12 & 16 & 750 \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table}
  \centering
  \caption{The numbers of instances (out of 1466) solved by ADDMC with each
    encoding (uniquely, faster than with others, and in total) under the
    described time and memory constraints}%
  \begin{tabular}{lrrr}
    \toprule
    Encoding & Unique & Fastest & Total \\
    \midrule
    \texttt{cd05} & 2 & 3 & 380 \\
    \texttt{cd06} & 0 & 0 & 363 \\
    \texttt{cw} & 234 & 935 & 980 \\
    \texttt{d02} & 40 & 111 & 797 \\
    \texttt{sbk05} & 12 & 44 & 765 \\
    \bottomrule
  \end{tabular}
\end{table}
% TODO: another observation: cw was the fastest in 935 out of the 980 instances
% that it solved (95.4%)
